### 2024-08-24 paper.tex
improve dimension calculation

\begin{lemma}
    \(\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - something\).
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    First we compute
    \[\gamma(L) - \gamma(s(L)) = \sum_{i : \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}).\]
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_{k + 1}} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    Now we consider how to get from \(L'\) to \(s(L')\).
    Sorting \(L'\) just requires shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(s(L')\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(s(L')) - \gamma(L') = \]
    \[\sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    TODO: the thing above would be cleaner if \(p_{i_0} := 0\).
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(s(L))] + [\gamma(s(L')) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
        something
    \end{align*}

>>>>

\begin{lemma}
    \(\gamma([\mu_1, ..., \mu_l]) = \gamma([0, \lambda_1, ..., \lambda_k]) - something\).
\end{lemma}
\begin{proof}
    Let \(L = [q_{i_0}, \lambda_1, ..., \lambda_k]\).
    Note that \(\mu = [..., q_{i_0} + p_{i_1}, ..., q_{i_1} + p_{i_2}, ..., ..., q_{i_r} + p_{i_{r + 1}}, ...]\).
    Let \(L'\) be the result of taking \(\mu\) and, for each \(x\), replacing one occurence of \(q_{i_x} + p_{i_{x + 1}}\) by \(q_{i_x} + p_{i_x}\); that is,
    \(L' = [..., q_{i_0}, ..., q_{i_1} + p_{i_1}, ..., q_{i_2} + p_{i_2}, ..., q_{i_r} + p_{i_r}]\).
    Note that we get from \(\mu\) to \(L'\) by just moving each \(p_{i_k}\) to the right by \(1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}\) slots.
    So,
    \[\gamma(L') - \gamma(\mu) = \sum_{k = 1}^r p_{i_{k + 1}} (1 + \#\{i \notin I : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}) = \]
    \[\sum_{k = 1}^r p_{i_k} \cdot \#\{i : q_{i_{k - 1}} + p_{i_k} > \lambda_i \geq q_{i_k} + p_{i_{k + 1}}\}.\]
    Now we consider how to get from \(L'\) to \(L\).
    First we shift \(q_{i_0}\) to the left by \(\#\{i \notin I : \lambda_i \geq q_{i_0} + p_{i_1}\}\) slots.
    Then we leave \(q_{i_0}\) in place and sort the rest of the list.
    This entails shifting each \(q_{i_x} + p_{i_x}\) to the left by \(\#\{i \notin I : q_{i_x} + p_{i_x} > \lambda_i \geq q_{i_x} + p_{i_{x + 1}}\}\) slots.
    Shifting \(q_{i_x} + p_{i_x}\) to the left one slot, by swapping it with \(\lambda_i\), changes the value of \(\gamma\) by \(\lambda_i - (q_{i_x} + p_{i_x})\).
    To go from \(L'\) to \(s(L')\), we can just make these swaps repeatedly.  
    So,
    \[\gamma(L) - \gamma(L') = \]
    \[\sum_{i \notin I : q_{i_0} + p_{i_1} > \lambda_i \geq q_{i_0}} (\lambda_i - q_{i_0}) + \sum_{k = 1}^s \sum_{\{i \notin I : q_{i_k} + p_{i_{k + 1}} > \lambda_i \geq q_{i_k} + p_{i_k}\}} (\lambda_i - (q_{i_k} + p_{i_k})).\]
    TODO: the thing above would be cleaner if \(p_{i_0} := 0\).
    \par Now,
    \begin{align*}
        \gamma(L) - \gamma(\mu) & = \\
        [\gamma(L) - \gamma(L')] + [\gamma(L') - \gamma(\mu)] & = \\
    \end{align*}    
\end{proof}
